Large Language Models in Reinforcement Learning - A Comparison of Methods

### 2023-11-09 doc/paper.tex
smolfiks

With no intermediate rewards, more complex environments like the one shown in Figure \ref{unlockpickupenv} quickly become difficult to learn for traditional RL methods. Some environments can only be effectively solved by relying on language (for example, environments where the goal text describes a specific object to be picked up, which changes every time), while others can be solved without (for example, if the goal always is to pick up a key). We only use environments that can be solved without language, so that the baseline PPO algorithm is not at an unfair disadvantage.

@@

\subsection{Societal Impact and Potential Harmful Consequences}

@@

\subsection{Impact Mitigation Measures}

>>>>

With no intermediate rewards, more complex environments like the one shown in Figure \ref{unlockpickupenv} quickly become difficult to learn for traditional RL methods. In addition, some environments can only be effectively solved by relying on language (for example, environments where the goal text describes a specific object to be picked up, which changes every time), while others can be solved without (for example, if the goal always is to pick up a key). We only use environments that can be solved without language, so that the baseline PPO algorithm is not at an unfair disadvantage.

@@

\subsection*{Societal Impact and Potential Harmful Consequences}

@@

\subsection*{Impact Mitigation Measures}
